Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-29 ms.tex
Replace figures with journal compatible names
From faebaa2:
============

Add renamed figures f1.eps, f2.eps to git repo

In ms.tex,

(*) Replace first figure to f1.eps
(*) Replace second figure to f2.eps
Cite private communication from Randall Wayth
From 1a02743:
============

In ms.tex,

(*) Cite private communication from Randall Wayth
(*) Update the included ms.bbl info

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}). The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight. White dotted lines are the horizon delay limits. Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top). Power near the horizon limits caused by wide-field effects are prominent. Faint horizontal features at $\tau\simeq\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz. \label{fig:delay-spectra}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
\caption{Delay power spectra on three antenna spacings oriented northward, obtained by coherent averaging of 12 snapshots aligned in LST. The averaged data and models are shown in black and red respectively. The antenna spacings are 83.5~m ({\it top}), 104.2~m ({\it middle}), and 171~m ({\it bottom}). The horizontal dotted line is the {\it rms} of thermal fluctuations. The vertical dashed lines denote the horizon delay limits. The vertical dotted-dashed lines at $\tau = \pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz. The peaks close to the horizon delay limits are distinctly visible at $\sim 10$-1000~$\sigma$ levels. Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern. \label{fig:3-baseline-comparison-delay-spectra}}
\end{figure}

@@

Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon. This has important implications for instrument design and data analysis of future instruments such as HERA and SKA. For instance, SKA plans to use ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of pseudo-randomly placed vertical log-periodic dipole arrays. The ``station beam'' will be obtained by a phased addition of the dipole responses. The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith. HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA. Details of both telescopes are being finalized. Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.

>>>>

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{multi_baseline_fhd_sim_visibilities_amplitudes_comparison_185.0_MHz_30.7_MHz.eps}
\includegraphics[width=\linewidth]{f1.eps}
\caption{Delay power spectra obtained from a single snapshot ({\it top}), by averaging 12 snapshots of LST aligned MWA data ({\it middle}), and from modeling with no thermal noise added ({\it bottom}). The $x$-axis, denoted by $|\boldsymbol{b}|$ (and $k_\perp$), represents angular (and spatial) scales in the plane of the sky while the $y$-axis, shown in $\tau$ and $k_\parallel$, denotes the spatial scales along the line of sight. White dotted lines are the horizon delay limits. Dynamic range in the delay power spectra of MWA data has increased by a factor $\sim 10$ after averaging (middle) relative to that in a single snapshot (top). Power near the horizon limits caused by wide-field effects are prominent. Faint horizontal features at $\tau\simeq\pm 0.78\,\mu$s are visible due to effective lowering of thermal fluctuations and are the response to periodic coarse band edge flagging of MWA data every 1.28~MHz. \label{fig:delay-spectra}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{3_baseline_comparison_CLEAN_fhd_avg_visibilities_amplitudes_185.0_MHz_30.7_MHz.eps}
\includegraphics[width=\linewidth]{f2.eps}
\caption{Delay power spectra on three antenna spacings oriented northward, obtained by coherent averaging of 12 snapshots aligned in LST. The averaged data and models are shown in black and red respectively. The antenna spacings are 83.5~m ({\it top}), 104.2~m ({\it middle}), and 171~m ({\it bottom}). The horizontal dotted line is the {\it rms} of thermal fluctuations. The vertical dashed lines denote the horizon delay limits. The vertical dotted-dashed lines at $\tau = \pm 0.78\,\mu$s correspond to grating responses of periodic flagging of bandpass at intervals of 1.28~MHz. The peaks close to the horizon delay limits are distinctly visible at $\sim 10$-1000~$\sigma$ levels. Differences between model and data are primarily attributed to uncertainties in the foreground model and the MWA tile power pattern. \label{fig:3-baseline-comparison-delay-spectra}}
\end{figure}

@@

Using deeper MWA data, we have confirmed with high significance the earlier prediction that wide-field EoR measurements suffer significant foreground contamination from near the horizon. This has important implications for instrument design and data analysis of future instruments such as HERA and SKA. For instance, SKA plans to use ``stations'' of $\sim$~35~m diameter that act as aperture arrays consisting of pseudo-randomly placed vertical log-periodic dipole arrays. The ``station beam'' will be obtained by a phased addition of the dipole responses. The typical horizon response of these station beams is $\gtrsim$~30~dB lower than at the zenith (private communication from R.~Wayth). HERA will use dishes that limit response near the horizon to $\lesssim -40$~dB, $\sim$~20~dB lower than that of the MWA. Details of both telescopes are being finalized. Precise modeling is thus required to gain a complete understanding of the characteristics of the cosmological signal and the foregrounds.
